\textbf{EECS 340: Assignment 2}

### 2020-02-03 assignment_2/article.tex
🐛 Correct Problem 1(c1) with a lot of work goes to nothing :\ .

Since it is given that $\log(f(n)), \log(g(n)) \geq 0$, thus we must have:

\paragraph{Case 1} Assume $\log (g(n_{0})) \neq 0$:

Thus we may conclude $log(f(n)) = O(\log(g(n))$ for this case.

\paragraph{Case 2} Assume $\log (g(n_{0})) = 0$:

Since $\log (g(n_{0})) = 0$, we shall infer that $g(n_{0}) = 1$. We may arbitrarily pick some constants $c, c'$ where:

\begin{gather}
    \log c \leq 0 \nonumber\\
    \log c \leq (c' - 1) \cdot 0 \nonumber\\
    \log c \leq (c' - 1) \cdot \log(g(n_{0}))
\end{gather}

Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$. Putting this into the context of problem statement, we may have:

\begin{gather}
    \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$} \nonumber \\
    \Rightarrow \log(f(n)) \leq (c' - 1) \cdot \log(g(n_{0})) + \log(g(n)) \nonumber \\
    \Rightarrow \log(f(n)) \leq (c' - 1) \cdot \log(g(n)) + \log(g(n)) \nonumber \\
    \Rightarrow \log(f(n)) \leq c'\log(g(n))
\end{gather}

Thus we may conclude $log(f(n)) = O(\log(g(n))$ for this case.\newline

Since both cases reach to the conclusion of $log(f(n)) = O(\log(g(n))$, we have proven the statement to be valid.

>>>>

For $f(n) = 2$ and $g(n) = 1$, then $\log f(n) = 1$ and $\log g(n) = 0$. Since we cannot find any constant $c$ where:

\begin{gather}
    0 \leq 1 \leq c(0)
\end{gather}

Thus the statement is invalid.
